Healthcare professional's top priority is and should be patient healthcare. When it comes to human health, various aspects are time sensitive. Digitalising records in several other industries has sped things up and helped workers focus on more important tasks at work rather than mere documentation. Below we have enlisted some of our key features that would help reel in investors and sponsors:
By developing this charting software, we hope to assist healthcare professionals with charting activities. 
Lab work and charts are crucial for patient care to ensure patients receive appropriate care as and when required. Thus by digitalizing the charts and working on deep learning and AI models we hope to provide a quick and efficient solutions to health care professionals where time is of the essence. 
Doctors also have to follow through with hospital hierarchies and protocols before administering drugs and necessary care activities. We plan on implementing voice authentication on our platform thereby establishing direct contact with the doctor and the patient physician.
Technical jargon is common across all industries and hospitals to have their own set of terms that they practice. We hope to bridge the gap between medicine and accounting by helping to translate the dosage of medication depending on patient vitals . This helps nurses safe time and focus on patient care instead of helping with billing and documentation. 
Our competitors are mainly other EHR systems like OpenEMR and Epic. Our unique selling points that sets us apart from our competitors is our feature that combines charting and billing system. Thus ,building an holistic web application. Our voice authentication also is step ahead towards efficiency and real-time patient and healthcare professional interaction. 
