\subsection{Health Information Technology for Economic and Clinical Health (HITECH) Act of 2009}
\subsubsection{Description}
Provides the HHS (US Dpt. of Health \& Human Services) authority to establish programs to improve health care quality, safety, and efficiency through the promotion of health IT. This includes electronic health records and privately secured electronic health information exchange.
\subsubsection{Source}
Index for Excerpts from the American Recovery and Reinvestment Act of 2009 (ARRA)
\subsubsection{Constraints}
MedTech EHR must employ "(2) ENTERPRISE INTEGRATION" meaning the electronic linkage of health care providers, health plans, the government, and other interested parties, to enable the electronic exchange and use of health information among all components of the health care infrastructure.
\subsubsection{Standards}
SEC. 13101. ONCHIT; STANDARDS DEVELOPMENT AND ADOPTION. \cite{UnitedStatesCongress2009}
\subsubsection{Priority}
Moderate

\subsection{Health Insurance Portability and Accountability Act (HIPAA) of 1996}
\subsubsection{Description}
This protects health insurance coverage for workers and their families when they change or lose their jobs, requires the establishment of national standards for electronic health care transactions, and requires establishment of national identifiers for providers, health insurance plans, and employers.
\subsubsection{Source}
HEALTH INSURANCE PORTABILITY AND ACCOUNTABILITY ACT OF 1996 Public Law 104-191 104th Congress
\subsubsection{Constraints}
Patients must have insurance entries and will be viewed for money billing and transactions.
\subsubsection{Standards}
TITLE XXVII--ASSURING PORTABILITY, AVAILABILITY, AND RENEWABILITY OF HEALTH INSURANCE COVERAGE \cite{Caplan2003}
\subsubsection{Priority}
Low