Medtech is mainly a software project that will not require the use of laboratory equipment.

\subsection{Laboratory equipment lockout/tagout (LOTO) procedures}
\subsubsection{Description}
Any fabrication equipment provided used in the development of the project shall be used in accordance with OSHA standard LOTO procedures. Locks and tags are installed on all equipment items that present use hazards, and ONLY the course instructor or designated teaching assistants may remove a lock. All locks will be immediately replaced once the equipment is no longer in use.
\subsubsection{Source}
CSE Senior Design laboratory policy
\subsubsection{Constraints}
Equipment usage, due to lock removal policies, will be limited to availability of the course instructor and designed teaching assistants.
\subsubsection{Standards}
Occupational Safety and Health Standards 1910.147 - The control of hazardous energy (lockout/tagout).
\subsubsection{Priority}
Non-existent

\subsection{No inaccuracies of charted data}
\subsubsection{Description}
For legal reasons and patient safety, charted data must be absolutely accurate and must be double checked. Charted data includes medication orders for the correct drug and its prescription.
\subsubsection{Source}
The Office of the National Coordinator for Health Information Technology, Reducing Medication Errors: Simple Recommendations
\subsubsection{Constraints}
Software usage may be limited without training or reference to a nurse's inputs.
\subsubsection{Standards}
Tools: Reducing Pick List Errors in Medication Ordering for Providers \cite{AndrewGettinger2016}
\subsubsection{Priority}
High

