According to Capterra, a software research group,  30\% of unsatisfied users noted that their EHR software was difficult to use \cite{Reisenwitz2015}. This stems from navigation issues where the user has to actively find what he/she is looking for, looking into menus, tabs, and often for a long period of time. This has been an issue because they lack specialty specific interfaces. Current EHRs attempt to combine multiple professions into one, which can put stress on one profession to navigate through to find relevant information. \cite{Monica2018}

One solution that was considered was data visualization. In a 2017 study from the University of Illinois at Chicago, they were determining if data visualization benefits healthcare since it is a complex field with many specializations. They do not have an explicit solution, since they concluded that data visualization is in its infancy in healthcare. By having the users interact with visualizations, they create new knowledge applicable to them. From their example, a patient's pain score from 1 to 10 could indicate many things. For a physician, additional medicine may be needed. For a nurse, this may register as a failure in pain management. For a physical therapist, this may indicate the pain came from a therapy session. Either all, some, or none could be correct. By visualizing this through glyphs, colors, and shapes, it could portray more information than data values.
\cite{Boyd2017}

In a study published in the Journal of the American Board of Family Medicine, they compared different physician EHR note designs to determine which design is most efficient for physicians. "Cluttered documentation may contribute adversely to physician readers’ cognitive load, inadvertently obscuring high-value information with less valuable information", researchers noted \cite{Monica2017}. They discovered that physicians did not like the traditional SOAP EHR note design, SOAP standing for: Subject, Objective, Assessment, Plan. Simple modifications, such as using colored text and bold fonts or reorganizing Assessment and Plan to the top, could be used to highlight important information. Hiding irrelevant data also avoids overwhelming physicians with clutter.
 \cite{Belden2017}
 
 These studies are explaining high level concepts and there is also the factor of company licenses and privacy, so finding specific solutions that EHR software implemented can be difficult to find. However, the studies will aid us in the design of the user interface.